2.4: OLS: Goodness of Fit and Bias

### 2019-09-26 content/class/10-class.Rmd
Update class 10; tweak 10 slides

Today we start looking at *associations* between variables, which we will first attempt to quantify with measures like *covariance* and *correlation*. Then we turn to fitting a line to data via *linear regression*. We overview the basic regression model, the parameters and how they are derived, and see how to work with regressions in `R` with `lm` and the tidyverse package [`broom`](https://broom.tidyverse.org/).

We consider an extended example about class sizes and test scores, which comes from a (Stata) dataset from an old textbook that I used to use, [Stock and Watson, 2007](https://www.pearson.com/us/higher-education/product/Stock-Introduction-to-Econometrics-Update-3rd-Edition/9780133486872.html?tab=resources). Download and follow along with the data from today's example:^[Note this is a `.dta` Stata file. You will need to (install and) load the package `haven` to `read_dta()` Stata files into a dataframe.]

@@

- [<i class="fas fa-external-link-square-alt"></i> Lecture Slides](/slides/09-slides.html)

# Assignments: Problem Set 1 DUE and Problem Set 2

[Problem Set 1](/assignment/01-problem-set.html) answers will be posted shortly, and the graded assignment emailed back to you.^[Sorry I've been too busy to send emails confirming that I recieved your problem set!]

[Problem Set 2](/assignment/01-problem-set.html) (on classes 2.1-2.2) is due by Thursday September 26.

>>>>

Today we continue looking at basic OLS regression. We will cover how to measure if a regression line is a good fit (using $R^2$ and $\sigma_u$ or SER), and whether OLS estimators are *biased*. These will depend on four critical *assumptions about $u$.*

In doing so, we begin an ongoing exploration into inferential statistics, which will finally become clear in another week. The most confusing part is recognizing that there is a *sampling distribution of each OLS estimator*. We want to measure the center of that sampling distribution, to see if the estimator is *biased*. Next class we will measure the spread of that distribution.

We continue the extended example about class sizes and test scores, which comes from a (Stata) dataset from an old textbook that I used to use, [Stock and Watson, 2007](https://www.pearson.com/us/higher-education/product/Stock-Introduction-to-Econometrics-Update-3rd-Edition/9780133486872.html?tab=resources). Download and follow along with the data from today's example:^[Note this is a `.dta` Stata file. You will need to (install and) load the package `haven` to `read_dta()` Stata files into a dataframe.]

@@

- [<i class="fas fa-external-link-square-alt"></i> Lecture Slides](/slides/10-slides.html)

# Assignments: Problem Set 2 DUE

[Problem Set 2](/assignment/01-problem-set.html) is DUE. Answers will be posted later today.

### 2019-09-26 static/slides/10-slides.Rmd
Update class 10; tweak 10 slides

```{r, echo = T}
# as ratio of variances
school_reg %>%
  augment() %>%
  summarize(r_sq = var(.fitted)/var(testscr)) # variance of *predicted* testscr over variance of *actual* teestscr
```

@@

- The CLT allows us to approximate the sampling distributions of $\hat{\beta_0}$ and $\hat{\beta_1}$ as normal
    - Generally agreed for $n>100$

>>>>

```{r, echo = T}
# as ratio of variances
school_reg %>%
  augment() %>%
  summarize(r_sq = var(.fitted)/var(testscr)) # var. of *predicted* testscr over var. of *actual* testscr
```

@@

- The CLT allows us to approximate the sampling distributions of $\hat{\beta_0}$ and $\hat{\beta_1}$ as normal
